How predictable is extinction?

### 2018-12-07 doc/intro.tex
passing intro

By studying how species vary in their extinction risk over time and we can assess which species are at greater risk under unobserved conditions. We that that extinction risk varies over time in both intensity (average rate) and selectivity (difference in risk between taxa).

By including and modeling this natural variation in extinction risk, we are able to improve our overall predictions because we incorporate and explictly model differences between observations from across a range of possible intensities and selectivies

or the intrisic risk of extinction -- all species can go extinct at any ``moment,'' what are the relative risks between groups and over time
if we gather the kinds of predictors that apparently matter, and use them to make specific predictions of extinction 
If we gather the kinds of predictors that have been found to correlate strongly with extinction risk, how well can we predict species extinction?

>>>>

By studying how species vary in their extinction risk over time and we can assess which species are at greater risk under unobserved conditions. We that that extinction risk varies over time in both intensity (average rate) and selectivity (difference in risk between taxa). Species, after all, can go extinct at any ``moment'' and the relative risk of extinction exhibited by different taxonomic groups and how that varies over time is an important dynamic which shapes the rate and structure of extinction. By including the kinds of biological and abiological predictors that have been shown to affect differences in extinction risk, we can improve our predictions of species extinction risk for a given set of conditions. Additionaly, by specifically including and modeling the temporal variation in extinction risk, we are able to improve our overall predictions because we incorporate and explictly model differences between observations from across a range of possible intensities and selectivies

Extinction studies have normally been focused on understanding how biological and abiological factors impact differences in extinction risk over time and between taxa CITATION.
